Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2021-02-19 Manuscript/HI_Model_ms.Rmd
updated manuscript files

### *4.1 Impact of different climate and land-use pathways* 
By comparing model results of Hawaiian ecosystem carbon balance under different scenario combinations, we were able to assess the relative impact of both global emissions reductions and regional actions to reduce emissions from land use, land use change, and disturbances such as wildland fire (figure 5). Global adherence to a lower emissions trajectory (i.e., switching from RCP 8.5 to RCP 4.5) had the largest cumulative impact, resulting in a median of 26 additional Tg C sequestered by Hawaiian ecosystems over the 90-year simulation period. Long-term reductions in the intensity of land-use change also consistently led to an increase in ecosystem carbon sequestration, but to a lesser degree than global emissions reductions. Switching from the ‘high’ to the ‘low’ land‐use scenario resulted in a median cumulative retention of an additional 11.6 Tg C in Hawaiian ecosystems by 2100. The combination of global climate mitigation and a reduction in land‐use conversions had the largest potential benefit to ecosystem carbon sequestration, reducing cumulative net losses by over 400% (37.7 Tg C). Notably,

>>>>

### *4.1 Impact of different climate and land-use pathways* 
By comparing model results of Hawaiian ecosystem carbon balance under different scenario combinations, we were able to assess the relative impact of both global emissions reductions and regional actions to reduce emissions from land use, land use change, and disturbances such as wildland fire (figure 5). Global adherence to a lower emissions trajectory (i.e., switching from RCP 8.5 to RCP 4.5) had the largest cumulative impact, resulting in a median of 26 additional Tg C sequestered by Hawaiian ecosystems over the 90-year simulation period. Long-term reductions in the intensity of land-use change also consistently led to an increase in ecosystem carbon sequestration, but to a lesser degree than global emissions reductions. Switching from the ‘high’ to the ‘low’ land‐use scenario resulted in a median cumulative retention of an additional 11.6 Tg C in Hawaiian ecosystems by 2100. The combination of global climate mitigation and a reduction in land‐use conversions had the largest potential benefit to ecosystem carbon sequestration, reducing cumulative net losses by over 400% (37.7 Tg C). Notably, the relative impact of reducing emissions from land-use change was much greater under the high radiative forcing pathway (RCP 8.5). Cumulative NBP increased by 130% when switching from the high to low land-use scenario under RCP 8.5, as opposed to a 37% cumulative increase in NBP when switching from high to low land-use under RCP 4.5.
